---
title: "Get files content"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get files content}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 4
)
```

Set connections to hosts.

> Example workflow makes use of public GitHub and GitLab, but it is plausible, that you will use your internal git platforms, where you need to define `host` parameter. See `vignette("set_hosts")` article on that.

```{r}
library(GitStats)

git_stats <- create_gitstats() %>%
  set_github_host(
    orgs = c("r-world-devs", "openpharma"),
    token = Sys.getenv("GITHUB_PAT")
  ) %>%
  set_gitlab_host(
    orgs = c("mbtests"),
    token = Sys.getenv("GITLAB_PAT_PUBLIC")
  )
```

With `GitStats` you can get the content of all text files in repo that are of your interest. First you need to get the files structure. You can pull specific types of files, by setting `pattern` with regular expression and `depth` with integer, which defines level of directories to look for the files.

```{r}
files_structure <- get_files_structure(
  gitstats_object = git_stats,
  pattern         = "\\.md",
  depth           = 1L,
  progress        = FALSE
)
dplyr::glimpse(files_structure)
```

Once you pull the files structure, `GitStats` will store it. If you run then `get_files_content()` function, by default it will make use of this structure (unless you define `file_path`, which will override saved files structure).

```{r}
files_content <- get_files_content(
  gitstats_object = git_stats,
  progress        = FALSE
)
dplyr::glimpse(files_content)
```
