---
title: "Get files content"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get files content}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 4
)
```

Set connections to hosts.

> Example workflow makes use of public GitHub and GitLab, but it is plausible, that you will use your internal git platforms, where you need to define `host` parameter. See `vignette("set_hosts")` article on that.

```{r}
library(GitStats)

git_stats <- create_gitstats() %>%
  set_github_host(
    orgs = c("r-world-devs", "openpharma"),
    token = Sys.getenv("GITHUB_PAT")
  ) %>%
  set_gitlab_host(
    orgs = c("mbtests"),
    token = Sys.getenv("GITLAB_PAT_PUBLIC")
  )
```

With `GitStats` you can get the content of all text files in repo that are of your interest. You can pull specific types of files, by setting `pattern` with regular expression and `depth` with integer, which defines level of directories to look for the files.

```{r}
files_structure <- get_files(
  gitstats = git_stats,
  pattern = "\\.md",
  depth = 1L,
  progress = FALSE
)
dplyr::glimpse(files_structure)
```
