---
title: "Get and store your data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get and store your data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 4
)
```

Set connections to hosts.

> Example workflow makes use of public GitHub and GitLab, but it is plausible, that you will use your internal git platforms, where you need to define `host` parameter. See `vignette("set_hosts")` article on that.

```{r}
library(GitStats)

git_stats <- create_gitstats() %>%
  set_github_host(
    orgs = c("r-world-devs", "openpharma"),
    token = Sys.getenv("GITHUB_PAT")
  ) %>%
  set_gitlab_host(
    orgs = c("mbtests"),
    token = Sys.getenv("GITLAB_PAT_PUBLIC")
  )
```

As scanning scope was set to `organizations` (`orgs` parameter in `set_*_host()`), `GitStats` will pull all repositories from these organizations.

```{r}
repos <- get_repos(git_stats, progress = FALSE)
dplyr::glimpse(repos)
```

You can always go for the lighter version of `get_repos`, i.e. `get_repos_urls()` which will print you a vector of URLs instead of whole table.

```{r}
repos_urls <- get_repos_urls(git_stats)
dplyr::glimpse(repos_urls)
```

## Verbose mode

If messages overwhelm you, you can switch them off in the function:

```{r}
release_logs <- get_release_logs(
  gitstats_object = git_stats,
  since = "2024-01-01",
  verbose = FALSE
)
dplyr::glimpse(release_logs)
```

Or globally:

```{r, eval = FALSE}
verbose_off(git_stats)
```

## Cache

After pulling, the data is saved to `GitStats`.

```{r}
commits <- get_commits(
  gitstats_object = git_stats,
  since           = "2024-06-01",
  until           = "2024-06-30",
  progress        = FALSE
)
dplyr::glimpse(commits)
```

Caching feature is by default turned on. If you run the `get_*()` function once more, data will be retrieved from `GitStats` object.

```{r}
commits <- get_commits(
  gitstats_object = git_stats,
  since           = "2024-06-01",
  until           = "2024-06-30"
)
dplyr::glimpse(commits)
```

Unless, you switch off the cache:

```{r}
commits <- get_commits(
  gitstats_object = git_stats,
  since    = "2024-06-01",
  until    = "2024-06-30",
  cache    = FALSE,
  progress = FALSE
)
dplyr::glimpse(commits)
```

Or simply change the parameters for the function:

```{r}
commits <- get_commits(
  gitstats_object = git_stats,
  since           = "2024-07-01",
  progress        = FALSE
)
dplyr::glimpse(commits)
```

## Storage

Finally, have a glimpse at your storage:

```{r}
git_stats
```
