---
title: "Get data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 4
)
```

Set connections to hosts.

> Example workflow makes use of public GitHub and GitLab, but it is plausible, that you will use your internal git platforms, where you need to define `host` parameter. See vignette("set_hosts") article on that.

```{r}
library(GitStats)

git_stats <- create_gitstats() %>%
  set_github_host(
    orgs = c("r-world-devs", "openpharma"),
    token = Sys.getenv("GITHUB_PAT")
  ) %>%
  set_gitlab_host(
    orgs = c("mbtests"),
    token = Sys.getenv("GITLAB_PAT_PUBLIC")
  )
```

By default your search preferences are set to `organizations` (`org`), which means that `GitStats` will pull all repositories from the organizations you specified in `set_*_host()`.

```{r}
get_repos(git_stats)
```

## Storage

After pulling, the data is saved to `GitStats`. Caching feature is by default turned on. If you run the `get_*()` function once more, data will be retrieved from `GitStats` object.

```{r}
get_repos(git_stats)
```

Unless, you switch off the cache.

```{r}
get_repos(git_stats, cache = FALSE)
```

## Verbose mode

If messages overwhelm you, you can switch them off.

```{r}
get_release_logs(git_stats, since = "2024-01-01", verbose = FALSE)
```

## Pull repositories with code

Apart from pulling all repositories from organizations, you can look for those that have a particular text in a `code blob`:

```{r}
github_stats <- create_gitstats() %>%
  set_github_host(
    orgs = c("r-world-devs", "openpharma"),
    token = Sys.getenv("GITHUB_PAT")
  )

get_repos(github_stats, with_code = "Shiny")
```
