---
title: "Getting repositories with specific code or files"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting repositories with specific code or files}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 4,
  message = FALSE
)
```

Apart from pulling all repositories from organizations, you can look for those that have a particular text in a `code blob`:

```{r, eval = FALSE}
library(GitStats)

github_stats <- create_gitstats() %>%
  set_github_host(
    orgs = c("r-world-devs", "openpharma"),
    token = Sys.getenv("GITHUB_PAT")
  ) %>%
  verbose_off()

repos_urls <- get_repos_urls(
  gitstats = github_stats,
  with_code = "shiny"
)
```

You can limit your search, as it is allowed with GitLab and GitHub API search endpoints, to certain files.

```{r, eval = FALSE}
repos_urls <- get_repos_urls(
  gitstats = github_stats,
  with_code =  c("purrr", "shiny"),
  in_files = c("DESCRIPTION", "NAMESPACE", "renv.lock")
)
```

You can also search for repositories with certain files (do not confuse `with_files` with `in_files`!).

```{r, eval = FALSE}
repos_urls <- get_repos_urls(
  gitstats = github_stats,
  with_files = c("renv.lock", "DESCRIPTION")
)
```

## Package usage

`GitStats` allows you to search for repositories which make use of certain R packages. This function scans repositories if they import packages (look for package name in `DESCRIPTION` or `NAMESPACE`) or if they load package with `library()` or `request()`.

```{r, eval = FALSE}
package_usage <- get_repos_with_R_packages(
  gitstats = github_stats,
  packages = c("shiny", "purrr"),
  split_output = TRUE
)
```
