---
title: "Get and store your data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get and store your data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 4
)
```

Set connections to hosts.

> Example workflow makes use of public GitHub and GitLab, but it is plausible, that you will use your internal git platforms, where you need to define `host` parameter. See `vignette("set_hosts")` article on that.

```{r}
library(GitStats)

git_stats <- create_gitstats() |>
  set_github_host(
    orgs = c("r-world-devs", "openpharma"),
    token = Sys.getenv("GITHUB_PAT")
  ) |>
  set_gitlab_host(
    orgs = c("mbtests"),
    token = Sys.getenv("GITLAB_PAT_PUBLIC")
  )
```

As scanning scope was set to `organizations` (`orgs` parameter in `set_*_host()`), `GitStats` will pull all repositories from these organizations.

```{r}
repos <- get_repos(git_stats, progress = FALSE)
dplyr::glimpse(repos)
```

You can always go for the lighter version of `get_repos`, i.e. `get_repos_urls()` which will print you a vector of URLs instead of whole table.

```{r}
repos_urls <- get_repos_urls(git_stats)
dplyr::glimpse(repos_urls)
```

## Local Storage

After pulling, the data is saved to `GitStats`.

```{r}
commits <- get_commits(
  gitstats = git_stats,
  since = "2024-06-01",
  until = "2024-06-30",
  progress = FALSE
)
dplyr::glimpse(commits)
```

Caching feature is by default turned on. If you run the `get_*()` function once more, data will be retrieved from `GitStats` object.

```{r}
commits <- get_commits(
  gitstats = git_stats,
  since = "2024-06-01",
  until = "2024-06-30"
)
dplyr::glimpse(commits)
```

Unless, you switch off the cache:

```{r}
commits <- get_commits(
  gitstats = git_stats,
  since = "2024-06-01",
  until = "2024-06-30",
  cache = FALSE,
  progress = FALSE
)
dplyr::glimpse(commits)
```

Or simply change the parameters for the function:

```{r}
commits <- get_commits(
  gitstats = git_stats,
  since = "2024-07-01",
  progress = FALSE
)
dplyr::glimpse(commits)
```

## Database Storage

For more permanent storage, you can set up a connection to your database with `set_postgres_storage()` function. Then, all data pulled with `get_*()` functions will be stored in the database and retrieved from there when you run the function again.

```{r, eval = FALSE}
git_stats <- git_stats |>
  set_postgres_storage(
    host = "hostname",
    port = 5432,
    dbname = "dbname",
    user = Sys.getenv("POSTGRES_USERNAME"),
    password = Sys.getenv("POSTGRES_PASSWORD"),
    schema = "git_stats"
  )

# Pulling and saving to database
git_stats |>
  get_commits(
    since = "2024-06-01",
    until = "2024-06-30",
    progress = FALSE
  )
```

Stored data is now not dependent on `GitStats` object but on database credentials. If you set up same credentials in another `GitStats` object, you will be able to retrieve data from the database with that object as well.

```r
new_git_stats <- git_stats |>
  set_postgres_storage(
    host = "hostname",
    port = 5432,
    dbname = "dbname",
    user = Sys.getenv("POSTGRES_USERNAME"),
    password = Sys.getenv("POSTGRES_PASSWORD"),
    schema = "git_stats"
  )

# Data is cached and retrieved instantly
new_git_stats |>
  get_commits(
    since = "2024-06-01",
    until = "2024-06-30",
    progress = FALSE
  )
```
