---
title: "GitStats workflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{GitStats workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 4
)
```

You can start by creating your `GitStats` object, where you will hold information on your multiple connections.

> Example workflow makes use of public GitLab, but is rather more plausible, that you will use your internal git platforms.

```{r}
library(GitStats)

git_stats <- create_gitstats() %>%
  set_host(
    api_url = "https://api.github.com",
    orgs = c("r-world-devs", "openpharma"),
    token = Sys.getenv("GITHUB_PAT")
  ) %>%
  set_host(
    api_url = "https://gitlab.com/api/v4",
    orgs = c("mbtests"),
    token = Sys.getenv("GITLAB_PAT_PUBLIC")
  )
```

If you have your token environment variables stored in `GITHUB_PAT` or `GITHUB_PAT_*` and `GITLAB_PAT` or `GITLAB_PAT_*` you do not need to specify them in `set_host()` function, `GitStats` will automatically find them.

```{r, eval = FALSE}
git_stats <- create_gitstats() %>%
  set_host(
    api_url = "https://api.github.com",
    orgs = c("r-world-devs", "openpharma")
  ) %>%
  set_host(
    api_url = "https://gitlab.com/api/v4",
    orgs = c("mbtests")
  )
```

## Repositories workflow

By default your search preferences are set to `organizations` (`org`), which means that `GitStats` will pull all repositories from the organizations you specified in `set_host()`.

```{r}
pull_repos(git_stats)
```

You can add to your repositories information on contributors.

```{r}
pull_repos_contributors(git_stats)
```

After you pulled the data you can retrieve the `stats` from it.

```{r}
repos_stats <- get_repos_stats(git_stats)
head(repos_stats)
```

Or just retrieve the output.

```{r}
repos <- get_repos(git_stats)
```

Finally, you can plot the statistics. By default `last_activity` is plotted for 10 repositories.

```{r}
gitstats_plot(repos_stats)
```

But, you can change it to other column, also you can choose number of repositories.

```{r, fig.height = 9}
gitstats_plot(
  stats_table = repos_stats,
  value_to_plot = "contributors_n",
  value_decreasing = FALSE,
  n = 60
)
```

If you work with interactive app, you can use a `plotly_mode`.

```{r}
gitstats_plot(repos_stats, plotly_mode = TRUE)
```

## Commits workflow

It is basically very similar to the repositories one, but you should specify additionally at least `date_from` parameter.

```{r, message = FALSE}
pull_commits(
  gitstats_obj = git_stats,
  date_from = "2022-01-01",
  date_until = "2023-08-31"
) %>% 
  get_commits_stats() %>% 
  gitstats_plot()
```

You can pull stats by `week` or `day`.

```{r}
get_commits_stats(
  gitstats_obj = git_stats,
  time_interval = "week"
) %>% 
  gitstats_plot()
```

You can also retrieve just the pulled output.

```{r}
commits <- get_commits(git_stats)
head(commits)
```

## Set

You can setup your search preferences, either to `org`, `team` or `phrase`. 

With settings you can also set your language and silence the output.

```{r}
set_params(
  gitstats_obj = git_stats,
  print_out = FALSE
)
```

### Team

If you wish to setup your search parameter to `team`, add your team members first:

```{r}
git_stats %>%
  set_team_member("Kamil Wais", "kalimu") %>%
  set_team_member("Krystian Igras", "krystian8207") %>%
  set_team_member("Karolina Marcinkowska", "marcinkowskak") %>%
  set_team_member("Kamil Koziej", "Cotau") %>%
  set_team_member("Maciej Banaś", "maciekbanas")
```

> If you have another logins on other git platform, you should pass them separately, e.g. `set_team_member("Maciej Banas", "maciekbanas", "banasm")`.

Then set the parameters accordingly.

```{r}
set_params(
  gitstats_obj = git_stats,
  search_param = "team",
  team_name = "RWD",
  print_out = FALSE
) 
```

Pull repositories or commits finally.

```{r}
pull_repos(git_stats) %>% 
  get_repos_stats() %>% 
  gitstats_plot()
```

```{r message = FALSE}
pull_commits(
  gitstats_obj = git_stats,
  date_from = "2022-01-01",
  date_until = "2023-08-31"
) %>% 
  get_commits_stats() %>% 
  gitstats_plot()
```

### Phrase

With `GitStats` you can look for the repos with a certain phrase in code blobs (you can not do it for the commits!).

```{r}
repos_stats <- set_params(
  gitstats_obj = git_stats,
  search_param = "phrase",
  phrase = "shiny",
  print_out = FALSE
) %>% 
  pull_repos() %>% 
  get_repos_stats()

head(repos_stats)
```

### Language

You can define a programming language in your settings.

```{r}
repos_stats <- set_params(
  gitstats_obj = git_stats,
  search_param = "org",
  language = "JavaScript",
  print_out = FALSE
) %>% 
  pull_repos() %>% 
  get_repos_stats()
head(repos_stats)
```

You can always get back to All languages.

```{r}
reset_language(git_stats)
```

## Reset your settings

If you wish to get back to default settings, run:

```{r}
reset(git_stats)
```
