---
title: "Introduction to GitStats"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to GitStats}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 4.5,
  fig.align = "center"
)
```

The purpose of this package is to gather statistics on the developers' activity from multiple git platforms, e.g. GitHub public, GitHub enterprise and GitLab. 

You can look through these platforms to search for activity by:

- your team,

- a keyword,

- owner/group of repositories.

# Getting started

You can start by creating your `GitStats` object, where you will hold information on your multiple connections.

```{r}
library(GitStats)
library(magrittr)

git_stats <- create_gitstats() %>%
  set_connection(
    api_url = "https://api.github.com",
    token = Sys.getenv("GITHUB_PAT"),
    orgs = c("openpharma", "r-world-devs")
  ) %>%
  set_connection(
    api_url = "https://gitlab.com/api/v4",
    token = Sys.getenv("GITLAB_PAT"),
    orgs = c("mbtests")
  ) 
```

You can set up your team to explore it's activity:

```{r}
git_stats %>%
  set_team(team_name = "RWD-IE",
           "galachad",
           "krystian8207",
           "kalimu",
           "marcinkowskak",
           "Cotau",
           "Maciej Banaś", "maciekbanas") %>%
  get_repos(by = "team") %>% 
  plot_repos(repos_n = 15)
```
