---
title: "Setting hosts"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Setting hosts}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 4
)
```

## Connect to GitHub and/or GitLab

To run `GitStats` you need first to set hosts.

To set connections try:

```{r}
library(GitStats)

git_stats <- create_gitstats() %>%
  set_github_host(
    orgs = c("r-world-devs", "openpharma"),
    token = Sys.getenv("GITHUB_PAT")
  ) %>%
  set_gitlab_host(
    orgs = c("mbtests"),
    token = Sys.getenv("GITLAB_PAT_PUBLIC")
  )
```

If you have your access tokens stored in environment variables with such names as `GITHUB_PAT` or `GITHUB_PAT_*` and `GITLAB_PAT` or `GITLAB_PAT_*` you do not need to specify them in `set_*_host()` functions, `GitStats` will automatically find them.

```{r, eval = FALSE}
git_stats <- create_gitstats() %>%
  set_github_host(
    orgs = c("r-world-devs", "openpharma")
  ) %>%
  set_gitlab_host(
    orgs = c("mbtests")
  )
```

If you wish to connect to internal GitHub or GitLab, you need to pass argument to `host` parameter. 

```r
git_stats <- create_gitstats() %>%
  set_github_host(
    host = "github.internal.com",
    orgs = c("org_1", "org_2", "org_3"),
    token = Sys.getenv("YOUR_GITHUB_PAT")
  ) %>%
  set_gitlab_host(
    host = "internal.host.com",
    orgs = c("internal_org"),
    token = Sys.getenv("YOUR_GITLAB_PAT")
  )
```

### Set repositories for searching scope

Instead of scanning whole organizations, you might be interested in scanning particular repositories. In that case pass a vector of full names of repositories to `repos` parameter while skipping `orgs`.

```{r, eval = FALSE}
git_stats <- create_gitstats() %>%
  set_github_host(
    repos = c("r-world-devs/GitStats", "r-world-devs/shinyCohortBuilder", "openpharma/DataFakeR")
  ) %>%
  set_gitlab_host(
    orgs = c("mbtests")
  )
```

### Set whole GitStats platforms to scan

This is possible in case of private hosts, as public ones are deemed to be too large. To set whole Git platform to be scanned just set hosts without specifying `orgs` or `repos`.

```r
git_stats <- create_gitstats() %>%
  set_github_host(
    host = "github.internal.com",
    token = Sys.getenv("YOUR_GITHUB_PAT")
  ) %>%
  set_gitlab_host(
    host = "internal.host.com",
    token = Sys.getenv("YOUR_GITLAB_PAT")
  )
```
