---
title: "Setting hosts"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Setting hosts}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 4
)
```


To make `GitStats` work you need to set hosts after creating `gitstats_object`.

You can set GitLab host with `set_gitlab_host()` and GitHub host with `set_github_host()` or both.

When setting hosts you need to take into account:

* Do you wish to connect to `private` or `public` hosts?

* What `scanning scope` do you wish to set? Do you want to scan specific `organizations` or `repositories` or maybe whole git platforms?

* Do you have `tokens` set up and stored in your environment variables that grant you access to APIs?

## Public and private hosts

If you connect to public hosts you simply call `set_github_host()` or `set_gitlab_host()` function without specifying `host` parameter.

```{r, eval = FALSE}
library(GitStats)
git_stats <- create_gitstats() %>%
  set_github_host(
    orgs = c("r-world-devs", "openpharma"),
    token = Sys.getenv("GITHUB_PAT")
  ) %>%
  set_gitlab_host(
    orgs = c("mbtests"),
    token = Sys.getenv("GITLAB_PAT_PUBLIC")
  )
```

If you wish to connect to internal GitHub or GitLab, you need to pass names of the hosts to `host` parameter. Remember also to have tokens set up properly for these hosts (on tokens read below).

```r
git_stats <- create_gitstats() %>%
  set_github_host(
    host = "github.internal.com",
    orgs = c("org_1", "org_2", "org_3"),
    token = Sys.getenv("YOUR_GITHUB_PAT")
  ) %>%
  set_gitlab_host(
    host = "internal.host.com",
    orgs = c("internal_org"),
    token = Sys.getenv("YOUR_GITLAB_PAT")
  )
```

### API versions

GitStats is configured to connect to GitHub API (version 3) and GitLab API (version 4).

## Scanning scope

When setting hosts you choose what scanning scope of your GitStats will be:

* `organizations/groups` - in this case you need to pass character arguments (names of organizations (in case of GitHub) or groups (in case of GitLab)) to `orgs` parameter.

```{r, eval = FALSE}
git_stats <- create_gitstats() %>%
  set_github_host(
    orgs = c("r-world-devs", "openpharma"),
    token = Sys.getenv("GITHUB_PAT")
  ) %>%
  set_gitlab_host(
    orgs = c("mbtests"),
    token = Sys.getenv("GITLAB_PAT_PUBLIC")
  )
```

* `repositories` - in this case you need to pass full names of repositories (`{org_name}/{repo_name}`) to the `repos` parameter.

```{r, eval = FALSE}
git_stats <- create_gitstats() %>%
  set_github_host(
    repos = c("r-world-devs/GitStats", "r-world-devs/shinyCohortBuilder", "openpharma/DataFakeR"),
    token = Sys.getenv("GITHUB_PAT")
  ) %>%
  set_gitlab_host(
    repos = "mbtests/gitstatstesting",
    token = Sys.getenv("GITLAB_PAT_PUBLIC")
  )
```

* `whole hosts` - this is possible for the time being only in case of private hosts, as public ones are deemed to be too large. To set whole Git platform to be scanned just set hosts without specifying `orgs` or `repos`. On the other hand, remember that to connect with internal host, you need to pass argument to `host` parameter.

```r
git_stats <- create_gitstats() %>%
  set_github_host(
    host = "github.internal.com",
    token = Sys.getenv("YOUR_GITHUB_PAT")
  ) %>%
  set_gitlab_host(
    host = "internal.host.com",
    token = Sys.getenv("YOUR_GITLAB_PAT")
  )
```

## Authorize your access with tokens

Remember to pass to your `set_*_host()` functions `tokens` that authorize access.

You can store your tokens in environment variables, e.g. defined in `.Renviron` file as `GITHUB_PAT` for GitHub and `GITLAB_PAT` for GitLab.

On how to create your tokens refer to GitHub API and GitLab API documentation.

When creating tokens you will be asked to set access scopes of the tokens. For `GitStats` to work you need tokens with given scopes:

- [GitHub] `public_repo`, `read:org` and `read:user`,
- [GitLab] `read_api`.

If you have your access tokens stored in environment variables with such names as `GITHUB_PAT` or `GITHUB_PAT_*` and `GITLAB_PAT` or `GITLAB_PAT_*` you do not need to specify them in `set_*_host()` functions, `GitStats` will automatically find them.

```{r, eval = FALSE}
git_stats <- create_gitstats() %>%
  set_github_host(
    orgs = c("r-world-devs", "openpharma")
  ) %>%
  set_gitlab_host(
    orgs = c("mbtests")
  )
```
